Evaluate PEER in each cohort and brain region

### 2020-11-23 combined_analysis/eval_resid_in_each.Rmd
add CTS

@@

    # upload observed expression
    file = paste0('geneExpr_',gsub(" ", '', gsub("-", "_", datID)), ".RDS")
    storeData( vobj$E, file, paste0(datID, " Observed expression"))

    # upload latent variables
    file = paste0('PEER',gsub(" ", '', gsub("-", "_", datID)), ".RDS")
    storeData( latentVariables, file, paste0(datID, " Latent variables for QTL analysis"))
  }
}
```

>>>>

    CT = dimnames(geneExpr)[[2]][i]

@@

    # upload observed expression
    file = paste0('geneExpr_',gsub(" ", '', gsub("-", "_", datID)), '_', CT,".RDS")
    storeData( vobj$E, file, paste0(datID, " Observed expression", '_', CT,))

    # upload covariate matrix
    file = paste0('covariateMatrix_',gsub(" ", '', gsub("-", "_", datID)), '_', CT, ".RDS")
    storeData( cov_matrix, file, paste0(datID, " Covariates for QTL analysis", '_', CT,))

    # upload latent variables
    file = paste0('PEER',gsub(" ", '', gsub("-", "_", datID)), '_', CT, ".RDS")
    storeData( latentVariables, file, paste0(datID, " Latent variables for QTL analysis", '_', CT,))
  }
}
```
